Verifying Cache Coherence Protocols for an infinite family of cache hierarchies

### 2014-02-06 paper/Intuition.tex
this the the correct version

\subsection{First level invariants}
Intuitively our protocol is correct because it guarantees that at most one
cache can handle a store request at a time, and that any cache that attempts to
handle a load request has the ``latest'' value. We can state this formally with
the following 4 invariants.

@@

\subsection{Second-level Invariants}
\label{second-level}

While Invariant \fullref{processReq} and \fullref{noReqAgain} can be seen
directly from the MSI transitions, correctness of Invariants
\fullref{localCompatibility} and \fullref{latestValue} require further
decomposition. We present 4 more invariants for proving those two invariants.

>>>>

\subsection{First level invariants}
\label{firstLevel}
Intuitively our protocol is correct because it guarantees that at most one
cache can handle a store request at a time, and that any cache that attempts to
handle a load request has the ``latest'' value. We can state this formally with
the following 4 invariants.

@@

\subsection{Second-level Invariants}
\label{secondLevel}

While Invariant \fullref{processReq} and \fullref{noReqAgain} can be seen
directly from the MSI transitions, correctness of Invariants
\fullref{localCompatibility1}, \fullref{localCompatibility2} and \fullref{latestValue} require further
decomposition. We present 4 more invariants for proving those two invariants.
